---
title: "Desarrollo Quiz 4"
author: "Pachamaltese"
date: "June 16, 2015"
output: html_document
---

#QUESTION 1
Consider the space shuttle data ?shuttle in the MASS library. Consider modeling the use of the autolander as the outcome (variable name use ). Fit a logistic regression model with autolander (variable auto) use (labeled as "auto" 1) versus not (0) as predicted by wind sign (variable wind). Give the estimated odds ratio for autolander use comparing head winds, labeled as "head" in the variable headwind (numerator) to tail winds (denominator).

```{r}
library(MASS)
data(shuttle)
## Make our own variables just for illustration
shuttle$auto <- 1 * (shuttle$use == "auto")
shuttle$headwind <- 1 * (shuttle$wind == "head")
fit <- glm(auto ~ headwind, data = shuttle, family = binomial)
exp(coef(fit)) #0.969
```

#QUESTION 2
Consider the previous problem. Give the estimated odds ratio for autolander use comparing head winds (numerator) to tail winds (denominator) adjusting for wind strength from the variable magn.

```{r}
shuttle$auto <- 1 * (shuttle$use == "auto")
shuttle$headwind <- 1 * (shuttle$wind == "head")
fit <- glm(auto ~ headwind + magn, data = shuttle, family = binomial)
exp(coef(fit)) #0.969
```

#QUESTION 3
If you fit a logistic regression model to a binary variable, for example use of the autolander, then fit a logistic regression model for one minus the outcome (not using the autolander) what happens to the coefficients?

The coefficients reverse their signs. Remember that the coefficients are on the log scale. So changing the sign changes the numerator and denominator for the exponent.

#QUESTION 4
Consider the insect spray data InsectSprays . Fit a Poisson model using spray as a factor level. Report the estimated relative rate comapring spray A (numerator) to spray B (denominator).

```{r}
fit <- glm(count ~ relevel(spray, "B"), data = InsectSprays, family = poisson)
exp(coef(fit))[2] #0.9457
```

#QUESTION 5
Consider a Poisson glm with an offset, t. So, for example, a model of the form glm(count ~ x + offset(t), family = poisson) where x is a factor variable comparing a treatment (1) to a control (0) and t is the natural log of a monitoring time. What is impact of the coefficient for x if we fit the model glm(count ~ x + offset(t2), family = poisson) where t2 <- log(10) + t ? In other words, what happens to the coefficients if we change the units of the offset variable. (Note, adding log(10) on the log scale is multiplying by 10 on the original scale.)

The coefficient estimate is unchanged. Note, the coefficients are unchanged, except the intercept, which is shifted by log(10). Recall that, except the intercept, all of the coefficients are interpretted as log relative rates when holding the other variables or offset constant. Thus, a unit change in the offset would cancel out. This is not true of the intercept, which is interperted as the log rate (not relative rate) with all of the covariates set to 0.

#QUESTION 6
Consider the data
```{r}
x <- -5:5
y <- c(5.12, 3.93, 2.67, 1.87, 0.52, 0.08, 0.93, 2.05, 2.54, 3.87, 4.97)
```
Using a knot point at 0, fit a linear model that looks like a hockey stick with two lines meeting at x=0. Include an intercept term, x and the knot point term. What is the estimated slope of the line after 0?

```{r}
z <- (x > 0) * x
fit <- lm(y ~ x + z)
sum(coef(fit)[2:3]) #1.013
```
