---
title: "Regression Models Project - Mauricio Vargas S."
output: html_document
---

##Short summary:
Does automatic transmission (among other variables) explain MPG in different car models?. To provide some light about this I have worked with R's cars database named Mtcars that contains different car models characteristics. In this report I can conclude that weight and cylinders are important variables and those (and not transmission) explain MPG in different car models. To answer this question I have used ANOVA which allows to determine if a variable can be dropped in a multivariated model.

##1st Step: Load data and determine principal variables:

```{r, results='hide'}
library(datasets) #This library provides free databases
data(mtcars) #The database I will use
str(mtcars) #str displays variables names and displays basic information
```
There are several variables in this dataset. ANOVA (analysis of variance) will be used to determine whose variables are relevant apart from transmission type. I will proceed from general to particular, so I won't lose generality after dropping variables.

##ANOVA
ANOVA explains the sources of variance so it can help to determine which variables have significant effects (statistically speaking). According to wikipedia: "In its simplest form, ANOVA provides a statistical test of whether or not the means of several groups are equal".
```{r}
analysis <- aov(mpg ~ ., data = mtcars) #I run ANOVA
summary(analysis) #this returns a summary containing relevant statistics
```
This analysis suggest I have to include CYL, DISP and WT within a linear model as those are significant variables. 

##2nd Step: Model's specification
I considered the following model (I provide the details and numbers at the end of the document) as I need to determine transmission and significant varibles effects over MPG:
```{r}
lm <- lm(mpg ~ cyl + wt + am, data = mtcars)
summary(lm)
```
AM is not significant and has a large p-value, but it is not possible to reject the hypothesis that the coefficient of AM is 0.

##3rd step: Box plot and residual plots
Automatic transmission versus manual transmission related to MPG (the question is to determine is transmission is a relevant variable to explain MPG). 
The residual is the difference between the observed data of the dependent variable $MPG$ and the fitted values $\widehat{MPG}$.
````{r}
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
par(mfrow=c(3,2))
par(mar=c(2.5, 5.5, 1.5, 1.5))
boxplot(mpg ~ am, data = mtcars, xlab = "AM (Transmission type)", 
        ylab = "MPG (Miles per galon)", main="Boxplot", xaxt="n", col=c("red","blue"))
axis(1, at=c(1,2), labels=c("automatic", "manual"))
par(mar=c(2.5, 5.5, 1.5, 1.5))
plot(lm)
```

As the boxes in the plot do not superpose it means automatic and manual cars are different. 

##4th: Conclusion
AM, WT and CYL are relevant variables that explain MPG. The $R^2$ is 0,83 so the model has a desirable goodness of fit and we can explain MPG related to the model's variables. AM by its own cannot explain MPG but is an important variable that explains (partially) car's performance.

\newpage

##APPENDIX: Descriptive statistics
In order to obtain an idea of how to proceed I considered the statistical momentums (mean, median, quartiles and variance-covariance matrix)
````{r}
summary(mtcars) #mean, median and quatiles
var(mtcars) #variance-covariance matrix
```

##APPENDIX: Model specification
If I take this model direct from ANOVA data:
```{r}
lm <- lm(mpg ~ cyl + disp + wt + am, data = mtcars)
summary(lm)
```
Then DISP is not significant, so there is evidence that the model can be improved by dropping variables as it is done with the final specification considered in this report.